Figures

### 2018-10-03 figures/01_county_extent.Rmd
caption and number cleanup

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
```

```{r read_explore_chunk, echo=FALSE, eval=TRUE}
knitr::read_chunk("../scripts/explore_lagos_ag.R")
```

@@

```{r county_extent, eval=TRUE, echo=FALSE, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (> 40%) and water quality data in LAGOS measured at > 3 sampling events between 1995 and 2005.", warning=FALSE, fig.width = 5.5, fig.height = 3}

>>>>

---
output: pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
```

```{r read_explore_chunk, echo=FALSE, eval=TRUE}
# setwd("figures")
knitr::read_chunk("../scripts/explore_lagos_ag.R")
```

@@

```{r 01_county_extent, eval=TRUE, echo=FALSE, fig.width = 5.5, fig.height = 3}
